\documentclass{article}
\usepackage{enumerate}
\usepackage[margin=.65in]{geometry}
\begin{document}
\title{History Reading assignment 12}
\author{Huy Le}
\maketitle
\section{ MainPoints}
\begin{enumerate}
\item Birmingham movements
\item Fidel Castro and United States relationship
\item Voting Rights Acts
\item The escalation in Vietnam
\item Antiwar movements
\item Betty Friedan and The Feminine Mystique
\end{enumerate}
\section{MainPoints Explained}
\subsection{ Birmingham movements}
- Spring 1963, demonstration took place in 186 cities, and 15,000 arrests.\\
- Luther King, one of the leader got arrested for nine days during these demonstrations\\
- In May, Luther King asked the schooled children to go to these demonstrations, The images and broadcast of violence that happened during these
demonstrations made a great impact in the community.\\
- Leading business men afraid of these demonstrations and promise to give jobs to black salespeople.

\subsection{Fidel Castro and United States relationship}
- Cuba was dependent on the U.S economically till Castro took power.\\
- Cuba Government started to nationalize American landholdings and also investment, then sold sugar to Soviet Union.\\
- This made Kennedy want to get rid of Castro. \\
- \textbf{The Bay of Pigs:} Kennedy allowed CIA to invade Cuba but turned out to be a total failure, the attempt made Cuba and Soviet stronger.


\subsection{Voting Rights Acts}
- in January 1965, King launched the voting rights campaign in Selma, Alabama, city of 355 of 15,000 black can vote.\\
- In March, despite the ban from the governor, King led a march to the state capital, state police assaulted them with prods, whips, and tear gas.\\
- the violence against non-violent demonstrators\\
- Johnson pressured Voting Right Act in 1965 and Twenty-fourth Amendment to the constitution outlawed the poll tax which prevent black to vote.

\subsection{The escalation in Vietnam}
- By 1968, number of Americans exceeded half a millions.\\
- Americans planes drop more tons of bombs more than the entire World War II.\\
- Americans spread chemicals and drop bombs like napalm\\

\subsection{Antiwar movements}
- By 1968, the war had damaged families, universities, and Democratic party apart.\\
- In 1967, King said that policy in Vietnam as an unconscionable use of violence and for draining resources from needs at home\\
- 1967, young men were burning their draft cards and fleeing to Canada to avoid fighting for the war they consider unjust.\\
- October of 1967, 100,000 Antiwar protesters assembled at the Lincoln Memorial. They placed flowers in the rifle barrels of soldiers guarding the nerve center of the American. 

\subsection{Betty Friedan and The Feminine Mystique}
- in 1963 Betty Friedan wrote The Feminine Mystique\\
- she painted a devastating picture in which talented, educated women trapped in a world that viewed marriage and motherhood as their primary goals.\\
- Some of organization and policy to help women in that enumerate
\begin{enumerate}
	\item Equal Pay Act: barring sex discrimination among holders of the same jobs.
	\item Civil Rights Act of 1964 prohibited the inequalities based on sex as well as race.
	\item Equal Employment Opportunity Commission established by the law became major force to break down barriers to female employment.
	\item NAtional organization for Women (NOW) was formed with Friedan as the president.
\end{enumerate}
\end{document}