\documentclass{article}
\usepackage{enumerate}
\usepackage[margin=.65in]{geometry}
\begin{document}
\title{History Reading Assignment 13}
\author{Huy Le}
\maketitle
\section{Main points in the reading}
\begin{enumerate}[(1)]
	\item President Nixon
	\item Sexual Revolution in Nixon years
	\item Carter's policies
	\item Ronald Reagan's tax reform
	\item Reagan and Conservative relations
	\item Reagan's relationship with Mikhail Gorbachev
\end{enumerate}

\section{Main Points Explain}

\subsection{President Nixon}
- He promoted a Family Assistance Plane that would replace Aid to families with dependent children. His plan failed to win approval by Congress.\\
- Nixon pursued the Philadelphia plan that required that construction contractors on federal project to hire specific numbers of minority workers in order to upgrade the minority employment. He later abandoned the Philadelphia plan in order to prepare for his reelection.\\
- Nixon supported the dictatorial pro-American regimes in Iran, Philippines, and South Africa. \\
- Chile in 1970, CIA killed Salvador Allende and give Augusto Pinochet the bloody dictatorship.\\
- Nixon visited China in 1972 leading to China taking up a seat at United Nations.\\
- Nixon also was the first American to visit Soviet Union, signed the Anti-Ballistic Missile Treaty that banned development of systems designed to intercept incoming Missiles, so that neither side would  be tempted to attack the other without fearing devastating retaliation.\\
- The biggest issue to Nixon presidency is Vietnam. With the protest against the war from back home, the corruption in soldiers, and many details about the brutality of the war is revealed on the news. Nixon finally had to remove the troops from Vietnam.\\
- Nixon became the first and only president of United States that have to resign because of the \textbf{Watergate incident}: five employee of Nixon's reelection committee took part in a break-in at Democratic Party headquarter in the Watergate department to install listening device.

\subsection{Sexual Revolution in Nixon years.}
- 1975, 1 millions of divorces \\
- American birth rate declined dramatically because of the availability of birth control and legal abortion.\\
- Congress approved title IX which banned gender discrimination in higher education.\\
- AT\&T entered an agreement in which it paid millions of dollar to workers who had suffered gender discrimination\\
- The gay and lesbian movement also developed at a new height.

\subsection{Carter's policies}
- He promoted human right foreign policies. For example, in 1978 he cut off the aid for military dictatorship governing Argentina.\\
- Carter believe that in the post-Vietnam era, American should focus on combating poverty, prevent the spread of nuclear weapons, promoting human rights instead of do everything to stop Communism.\\
- The Iran revolution with Khomeini overthrew the shah and also invaded the United States embassy made Carter seem helpless and inept and led to a rapid fail in his popularity.\\
- Afghanistan was occupied by Soviet was also a bad thing to his presidency.\\
- He lost the election in 1980 to Ronal Reagan. he received a 41 percent, a humiliating defeat for a sitting president.

\subsection{Ronald Reagan's tax reform.}
-  reduce the top tax rate from 70 percent to 50 percent.\\
- Tax reform Act reduced the rate on the wealthiest American to 28 percent\\
- The tax reform assume that it would inspire Americans to work harder because they would keep more of the money they earned.


\subsection{Reagan and Conservative relations.}
- He did very little to implement the conservative policies on economy or even social. \\
- Every thing stay in places like social security, Medicare , Medicaid, abortion stays legal, women keep entering the labor force.\\
- One rare victory for Conservative party is the Bowersv v. Hardwick in which the Supreme Court did uphold the constitutionality of state laws outlawing homosexual acts.

\subsection{Reagan's relationship with Mikhail Gorbachev}
- Reagen had very good relationship with the Soviet Union leader Mikhail Gorbachev.\\
- Gorbachev tried to have political openness and economic openness.\\
- Gorbachev also reduced the military budget of Soviet union significantly.\\
\end{document}