\documentclass{article}
\usepackage{enumerate}
\usepackage{setspace}
\begin{document}
\title{The Interview Projects}
\author{Huy Le}
\maketitle
\doublespacing
\begin{enumerate}

\item 
\textbf{\textit{What war did you attend ?}} \\
\textbf{Answer: } The war against the United States.
\item 
\textbf{\textit{How old were you when you enter the Vietnam war?}} \\
\textbf{Answer: } I was 18 year old when I attend the war in Vietnam against the United States.

\item 
\textbf{\textit{What is the motivation behind you when you enlisted?}} \\
\textbf{Answer: } That was the duty of every citizen when your country is at war.


\item 
\textbf{\textit{Did the North government force you to join the army or you volunteer?}} \\
\textbf{Answer: } He completely volunteered to join the army. You can't force us because we could run away when we in the army.

\item 
\textbf{\textit{Why did you choose the Communist side}} \\
\textbf{Answer: } Almost every citizen chose the Communist side to join, to me, it is like 99 \% of the Vietnamese support Communist side which was Ho Chi Minh.


\item 
\textbf{\textit{How many members of your family that joined the army are there? }} \\
\textbf{Answer: } There were three serving in the army, and one in the service force which helped out the Communist army.

\item 
\textbf{\textit{Was that war worth it to you back then?}} \\
\textbf{Answer: } I thought it was totally worth it. I'm afraid of death because the U.S was bombing the whole country, you couldn't hide any where. Therefore I joined the army.

\item 
\textbf{\textit{Did you see any one from your family while you were in the army?}} \\
\textbf{Answer: No, every one joined at differently at time, and they serve at different unites.}

\item 
\textbf{\textit{Was that war worth it to you now?}} \\
\textbf{Answer: } It is still worth now.  

\item 
\textbf{\textit{How did that war impact your family and you?}} \\
\textbf{Answer: } It didn't affect the family much because government took care of my family by giving foods, and money.

\item 
\textbf{\textit{did you write to your family regularly}} \\
\textbf{Answer: } Once in a while because the transportation from South to North at the time is very difficult.

\item 
\textbf{\textit{How long were your service?}} \\
\textbf{Answer: } It was 7 years and two months 

\item 
\textbf{\textit{Have you ever seen any capture or killing?}} \\
\textbf{Answer: } I've seen people got captured a lot but never seen any prisoners got killed.

\item 
\textbf{\textit{How was the conditions in the army in that time?}} \\
\textbf{Answer: } Very difficult, the army lacks of medicine, foods, clothes. People died easily because of diseases easily.


\item 
\textbf{\textit{What was the worst thing in the army in your experience?}} \\
\textbf{Answer: } When you see wounded soldiers from both sides but you can't help them and you have to watch them die slowly.  

\item 
\textbf{\textit{What was the thing you enjoyed the most in your experience?}} \\
\textbf{Answer: } Probably playing sport, like pingpong or volleyball tournament.

\item 
\textbf{\textit{How many people have you seen dying around you?}} \\
\textbf{Answer: } About 50 people, they die because of diseases, bombing, or poison from snakes, starvations, etc.

\item 
\textbf{\textit{What was the most intense experience?}} \\
\textbf{Answer: } When the B-52 attacked our base in 1969 in Tay Ninh city, I was hidding in the tunnel. There were a lot of people died even they stayed under the tunnel.

\item 
\textbf{\textit{It seems like the North Vietnam is very poor at that time, so how did you guy get food for the army?}} \\
\textbf{Answer: } The support from Soviet Union, China, and Cuba but we do produce a lot of rice to serve the army. The army also purchased a lot from Cambodia or even the South Vietnamese government.

\item 
\textbf{\textit{Does the government pay for your service}} \\
\textbf{Answer: } No, not at all. They have an account for me and I could purchase stuff using that account but no money. I could buy toothpaste, soaps,etc.

\item 
\textbf{\textit{When did you service end?}} \\
\textbf{Answer: } In December 1976.

\item 
\textbf{\textit{Why didn't you follow the South ? Why choose the North?}} \\
\textbf{Answer: } Because I followed Ho Chi Minh which is the right side. Uncle Ho was the right side because I learn from news, schools that he was the right leader for Vietnamese. 

\item 
\textbf{\textit{What do you think of the U.S army at the time? Do you hate them? Why ?}} \\
\textbf{Answer: } I really did hate them because they invaded our South Vietnam. They bombed our country and thought they can win because they were a big country with advance technology.  

\item 
\textbf{\textit{If you can choose to come back in time? What would you do differently like joining the South, not joining the army, or tried to achieve more in the army?}} \\
\textbf{Answer: } I would do the same thing. Nothing differently.

\item 
\textbf{\textit{Did the government give you benefits after the war ended? What are they?}} \\
\textbf{Answer: } About a few hundreds dollar. My kids got discounted for education. I got the army's insurance.

\item 
\textbf{\textit{How did you feel about North's victory in 1975}} \\
\textbf{Answer: } There was no surprise that we would have won the war because our people would keep fighting till the end no matter prices we have to pay.

\item 
\textbf{\textit{When did you get your wounds? Where?}} \\
\textbf{Answer: } in 1969 in Tay Ninh, My left eye and the back got wounded from the bombing. Another wound I got wound was when American army fought North Vietnam army in Cambodia. I got wounded by the bullets during the fight on my left hand and the back.

\item 
\textbf{\textit{Now you moved to the United States, What do you think about the Communist leaders back then, now, and do you want Communist to continue to exist in Vietnam? }} \\
\textbf{Answer: } Leaders in the past devoted their lives to the people, to the country. Leader nowadays in Vietnam abuse their power and stole from the people in Vietnam. They don't treasure the achievement we had. In the future, it is hard for our government to continue to exist because of the bad structure that limit development of production, relations, and economy. The Vietnamese need to find a better way to build our country.

\end{enumerate}
\end{document}